---
title: "Data aquisition"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Download data archive from [luftdaten.info](http://luftdaten.info) 

Function *luftdaten::LD_download()* saves data locally. 

Plot the size of data per day:
```{r cache=TRUE, eval=FALSE}
folder="/media/schmid/local/data/luftdaten/"
here=getwd()
system(paste0("cd ",folder,"; du -s * > ",here,"/size.txt"))
```
```{r show=TRUE}
size<-read.table(paste0(here,"/size.txt"), header=FALSE, col.names=c("size","date"))
size$date<-as.Date(size$date)
size$size<-size$size/(2^10)
plot(size$date,size$size, xlab="Date",main="Data per day", ylab="MB",type="s")
```

## Prepare database  (*mysqlite* using *RSQLite* package)

Use the following structure:
* lastedate
** lastedate: last date of input
* sensor
** locid: id of location/sensor (own)
** sensor_id: id of sensor (from data)
** sensor_type: type of sensor
** location: location id (from data)
** lat: latitude
** lon: longitude
* messungen
** id
** locid
** timestamp

```{r eval=FALSE}
library(RSQLite)
library(DBI)
db <- dbConnect(SQLite(), "db/luftdaten-temp.sqlite")
dbWriteTable(db,"lastdate",data.frame("lastdate"="2017-03-01"),overwrite=TRUE)
temp0<-data.frame("id"=integer(),"sensor_id"=integer(),"sensor_type"=character(),
                  "location"=integer(),"lat"=double(),"lon"=double())
dbWriteTable(db,"locid",temp0,append=TRUE)
temp0<-data.frame("id"=integer(), "locid"=integer(), "timestamp"=as.Date(character()))
dbWriteTable(db,"messungen",temp0,append=TRUE)
dbDisconnect(db)
```
```{r}
library(luftdaten)
library(RSQLite)
library(DBI)
db <- dbConnect(SQLite(), "db/luftdaten2018.sqlite")
tab<-dbListTables(db)
print(tab)
for (i in tab)print(dbListFields(db,i))
dbDisconnect(db)
```


## Save data to database. 

```{r ld_sql}
library(luftdaten)
library(RSQLite)
library(DBI)
db <- dbConnect(SQLite(), "/home/schmid/software/luftdaten/db/luftdaten2018.sqlite")
LD_sql(db, source="/media/schmid/local/data/luftdaten/",
       folder="/home/schmid/software/luftdaten", dbname="db/luftdaten2018")
dbDisconnect(db)
```

Script will tell us, if new measurement are found...

```{r}
library(luftdaten)
initializeDB("../db/temp",start="2018-01-01")
db <- dbConnect(SQLite(), "../db/temp.sqlite")
tab<-dbListTables(db)
print(tab)
for (i in tab)print(dbListFields(db,i))
dbReadTable(db,"lastdate")
dbDisconnect(db)
```

```{r}
db <- dbConnect(SQLite(), "../db/temp.sqlite")
LD_sql(db, end="2018/01/01", source="/media/schmid/local/data/luftdaten/",save=FALSE)
dbDisconnect(db)
```
```{r}
temp<-read.csv("/media/schmid/local/data/luftdaten/2018-01-01/2018-01-01_pms3003_sensor_368.csv",sep=";")
names(temp)
```
```{r}
db <- dbConnect(SQLite(), "../db/temp2.sqlite")
dbWriteTable(db,"test",data.frame("x"=7,"y"="c"))
dbWriteTable(db,"test",data.frame("x"=2,"Z"="klo"),append=TRUE)
```


```{r}
library(luftdaten)
library(DBI)
library(RSQLite)
initializeDB("db/2018",start="2018-01-01")
db <- dbConnect(SQLite(), "db/2018.sqlite")
LD_sql(db, end="2018/02/25", source="/media/schmid/local/data/luftdaten/",save=2,dbname="db/2018")
dbDisconnect(db)
```

library(luftdaten)
library(DBI)
library(RSQLite)
db <- dbConnect(SQLite(), "db/201617.sqlite")
LD_sql(db, end="2017/12/31", source="/media/schmid/local/data/luftdaten/",save=1,dbname="db/201617")
dbDisconnect(db)

